VM-Centric Snapshot Deduplication with Fault Isolation for Converged Cloud Architectures

### 2014-01-31 snapshot_system/paper_eval.tex
revise

\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
\end{small}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

Table~\ref{tab:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
then start to delete those snapshots one by one.
As we know the actual storage needs after each snapshot creation,
the storage leakage can be detected by
comparing the size of remaining data in use after deletion to the correct number.
The top dashed line is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while the solid line represents the actual average leakage measured during the experiment for all the VMs. 
The Bloom filter setting is based on $\Delta u/u=0.025$.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
there is only 1.5MB space leaked for every 1GB of stored data.
The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
to the  leakage under 5\%. 
This experiment shows that the leakage of our approximate snapshot deletion is very small, 
below the estimated number.

The space cost for deletion is insignificant.
Leakage repair needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM, 
when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.

>>>>

\comments{
 \begin{figure}
\vspace{-0.1in}
     \centering
     \includegraphics[width=3in]{figures/leakage}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{fig:leakage}
 \end{figure}
}
\begin{table}
\begin{small}
    \begin{tabular}{|c|c|c|c|c|c|}
    \hline
Del. step   &     1 &  3  & 5 & 7  & 9 \\ 
\hline   
     Estimated& .02\% & .06\% & .10\%& .14\% & .18\%\\ 
\hline   
     Measured & .01\% & .055\% & .09\% & .12\% & .15\% \\
\hline   
    \end{tabular}
\end{small}
     \caption{Accumulated storage leakage by approximate snapshot deletions ($\Delta u/u=0.025$)}
     \label{tab:leakage}
\end{table}

Table~\ref{tab:leakage} shows the average accumulated storage leakage in terms of percentage of
storage space per VM caused  by approximate deletions.
In this experiment, we select 1050 snapshots from 105 VMs and let all the VMs accumulate 10 snapshots, 
then start to delete 9 snapshots one by one.
As we know the actual storage needs after each snapshot creation,
the storage leakage can be detected by
comparing the size of remaining data in use after deletion to the correct number.
Row 1 in  Table~\ref{tab:leakage} 
is the deletion step. 3 means that version 3 is deleted. 
Row  2 is the predicted leakage using Formula~\ref{eq:leakrepair} from Section~\ref{sect:delete}
given $\Delta u/u=0.025$,
while Row 3 lists the actual average leakage measured during the experiment for all the VMs. 
The Bloom filter setting is based on $\Delta u/u=0.025$.
After 9 snapshot deletions, the actual leakage ratio reaches 0.0015 and this means that
there is only 1.5MB space leaked for every 1GB of stored data.
The actual leakage can reach  4.1\% after  245 deletions and such a repair is needed every 12 days
to the  leakage under 5\%. 
This experiment shows that the leakage of our approximate snapshot deletion is very small, 
below the estimated number.

The space cost for each snapshot deletion is insignificant.
Leakage repair for each VM needs less than 85MB of memory
considering each reference consumes 8 bytes plus  1 mark bit and  
each VM snapshot has 40GB backup data with about 10 million chunks. 
This VM-specific leakage  repair takes  less than half an hour for each VM, 
when disk bandwidth is controlled to 50MB/s. 
%When using the traditional mark-and-sweep~\cite{Guo2011,Fabiano2013} in VO for 2500 VMs, 
%a total of 212GB memory
%space on 100 node is accessed for processing each VM and each machine requires 2.12GB.
%To control the garbage growth, such a process needs to be conducted much more frequently than our
%VM-centric leakage repair.
